---
title: "PD Diagnosis Report"
author: "Janis Neumann"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme:
      version: 4
      bootswatch: flatly
    toc: true
---

```{r echo=FALSE, include=FALSE}

library(ggplot2)
library(viridis)
library(knitr)
library(kableExtra)

source("R/are_geom_split_violin.R")

```

---
### Data Overview

Parkinson's disease diagnoses in training, development and holdout data.
```{r echo=FALSE, fig.asp=1}
knitr::kable(tibble::tibble(report_input$cohort_table)) %>% 
  kableExtra::kable_styling(full_width = FALSE, position = "left")
```

```{r echo=FALSE, include=FALSE}
vio_p <- ggplot(report_input$clinical_data, aes(x = Gender, y = Age, fill = Group)) +
  geom_split_violin(scale = "count") +
  theme_bw() +
  scale_fill_viridis(alpha = 0.7, begin = 0.2, end = 0.8, discrete = TRUE, option = "D") +
  theme(legend.position="bottom") +
  facet_wrap(~ Data)
```

Age and gender distribution in training, development and holdout data.
```{r echo=FALSE, fig.asp=0.7}
vio_p
```

```{r echo=FALSE, include=FALSE}
pca_p <- ggplot(report_input$pca_pd,aes(x = V1, y = V2)) +
  geom_point(size = 2, aes(color = Group, shape = Gender)) +
  theme_bw() +
  xlab(paste0("PC 1 (", round(report_input$pca_imp[2, 1], 2)*100, "% of variance)")) +
  ylab(paste0("PC 2 (", round(report_input$pca_imp[2, 2], 2)*100, "% of variance)")) +
  theme(legend.position="bottom") +
  scale_color_viridis(alpha = 0.9, begin = 0.2, end = 0.8, discrete = TRUE, option = "D")
```

PCA of all three partitions of the data combined.
```{r echo=FALSE, fig.asp=1.1}
pca_p
```


### Model Performance

```{r echo=FALSE, include=FALSE}
roc_p <- ggplot(report_input$roc, aes(x = FPR, y = TPR)) +
  geom_line() +
  theme_bw()
```

ROC curve for development set predictions, shown for the model achieving the highest balanced accuracy (average of sensitivity & specificity).

```{r echo=FALSE, fig.asp=1}
roc_p
```

Performance metrics for the best model, selected based on development set performance.
```{r echo=FALSE, fig.asp=1}
knitr::kable(tibble::tibble(report_input$metrics)) %>% 
  kableExtra::kable_styling(full_width = FALSE, position = "left")
```

```{r echo=FALSE, include=FALSE}
cm_p <- ggplot(report_input$holdout_pred, aes(x = Observed, y = Predicted, color = Observed)) +
  geom_point(position = position_jitter(seed = 1, width = 0.4), aes(color = Observed)) +
  scale_shape_manual(values = c(1, 16)) +
  geom_hline(yintercept = 0.5) +
  theme_bw() +
  theme(legend.position = "none") +
  ylim(0, 1)
```

Predicted/Observed plot showing numeric values of model predictions.
```{r echo=FALSE, fig.asp=0.7}
cm_p
```
